\documentclass[a4paper,11pt]{moderncv}

\usepackage[british]{babel}
\usepackage{csquotes}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
%\usepackage{amsfonts}
%\usepackage{slantsc}
%\usepackage{microtype}
\usepackage{textcase}

\usepackage[sorting=ynt]{biblatex}
\usepackage{url}
\addbibresource{publications.bib}

\newcommand{\cvreference}[7]{%
  \textbf{#1}\newline% Name
  \ifthenelse{\equal{#2}{}}{}{\addresssymbol~#2\newline}%
  \ifthenelse{\equal{#3}{}}{}{#3\newline}%
  \ifthenelse{\equal{#4}{}}{}{#4\newline}%
  \ifthenelse{\equal{#5}{}}{}{#5\newline}%
  \ifthenelse{\equal{#6}{}}{}{\emailsymbol~\texttt{#6}\newline}%
  \ifthenelse{\equal{#7}{}}{}{\phonesymbol~#7}}

%\usepackage{hyperref}

\moderncvtheme{casual}
%\moderncvtheme{fancy}
%\moderncvtheme{banking}
%\moderncvtheme{classic}

%\setlength{\hintscolumnwidth}{45mm}
%\AtBeginDocument{\recomputelengths}

\firstname{Paulina}
\familyname{Abzieher, M.Phil.}
\title{Connecting NGOs to Translation Technology}
\address{Hammerschmidtgasse 9/7}{1190, Wien}
\mobile{+43 664 993 21 004}
\email{abziehp@tcd.ie}
%\extrainfo{Marié \\ beaucoup d'enfants}
%\photo{side-angle-single.png}

%\quote{}

\begin{document}

\maketitle

\section{Employment}

\cventry{2017 -- 2021}{Translation Project Manager/Partnership Success Manager}{Translators Without Borders}{Dublin}{}
{
  \textbf{Responsibilities:}
  \begin{itemize}
  \item \textbf{Account Management:} Advising international NGOs on how to meet their multilingual communication needs to achieve maximum impact.
  \item \textbf{Translation Project Management:} Overseeing and managing translation project team formation as well as content production and distribution.
  \item \textbf{Customer Support:} Prioritising, delegating and responding to translation project queries, both technical and organisational.
  \item \textbf{Volunteer Management:} Managing, overseeing and motivating volunteers involved in translation projects.
  \item \textbf{Training:} Training of clients and staff in the use of TWB's Kató community translation platform.
  \item \textbf{Staff Mentoring:} Mentoring and management of interns.
  \end{itemize}
}

\cventry{2012 -- 2017}{Communications and Community Coordinator}{The Rosetta Foundation}{Dublin}{}
{
  \textbf{Responsibilities:}
  \begin{itemize}
  \item \textbf{Platform Product Development:} Management of platform product development, coordinating developers at the University of Limerick with NGOs and translation volunteers to produce the Trommons community translation platform.
  \item \textbf{Quality Assurance:} Click testing and reporting of issues from the Trommons translation platform.
  \item \textbf{Communication Management:} Management of social media communications, press releases, website content and customer relations.
  \item \textbf{Community Management:} Multifunctional role encompassing NGO client and volunteer management as well as general administration, staff, office and donor management.
  \end{itemize}
}

\cventry{2010 -- 2012}{German Language Tutor}{Berlitz}{Dublin}{}
{
  \begin{itemize}
  \item Tuition, Language Testing and QA
  \end{itemize}
}

\cventry{2009 -- }{Freelance Translation}{English-German/German-English}{}{}
{
  \begin{itemize}
  \item Translation of literary and academic texts.
  \end{itemize}
}

\section{Education}

\cventry{2008 -- 2009}{M.Phil. Literary Translation}
{Trinity College Dublin}{Dublin}{}
{
  Graduated with First-Class Honours.
}
\cventry{2003 -- 2008}{BA Translation and Interpreting: German, English, Russian}{University of Vienna}{Vienna}{}{
  Graduated with First-Class Honours.
}

\section{Activism}

\cvlistitem{Founding member of SPARK single parent advocacy group.}
\cvlistitem{Founding member of Trinity College Dublin student parent society.}
\cvlistitem{Activist in Attac Ireland, housing and workers' rights campaigns.}

\section{References}

\cvreference{Anete Raugule}{Head of Translation and Interpreting}{}{NaTakallam}{}{anete.raugule@natakallam.com}{}

\cvreference{Alan Barrett}{Senior Developer}{}{The Rosetta Foundation/Translators Without Borders}{}{alanabarrett0@gmail.com}{}


\printbibliography[title=Translations]

\end{document}
